### 2021-02-13 introduction.tex
Add a catchy paragraph in the beginning of Introduction

>>>>

\todo[inline,author=FB]{Try to use the first page for something more flashy than exposure of saturation-based automated proving. Ideas: catchy puzzle-like example, abstract description of the crucial challenge etc.}

Choosing the next inference to apply is the most important decision point in the state-of-the-art
\todo{FB: Add "saturation-based"?}
\glspl{atp} for \gls{fol}.
Since the most popular \glspl{atp} use the superposition calculus with literal selection,
the \gls{sot}, such as the \gls{kbo}, plays a key role in guiding the proof search.
The \gls{kbo} is typically specified by a symbol precedence,
that is a permutation of the non-logical symbols of the input problem.
Each of the commonly used precedence heuristics orders the symbols
lexicographically according to a small number of simple symbol properties,
such as the number of occurrences in the input problem,
% vampire --symbol_precedence frequency
the arity of the symbol, or
% vampire --symbol_precedence arity
%occurrence in the conjecture,
% vampire --symbol_precedence_boost goal
%number of occurrences in unit clauses, or
% vampire --symbol_precedence_boost units
whether or not the symbol was introduced by the Tseytin transformation or skolemization.
% vampire --introduced_symbol_precedence top
Since none of the simple heuristics fits all the problems,
choosing a symbol precedence that guides the proof search on a problem efficiently towards the refutation
remains to be an intriguing task.
This paper explores the possibility of solving this task by training a neural networks
on the results of running the \gls{atp} Vampire \cite{10.1007/978-3-642-39799-8_1} with randomly sampled precedences.
